### 2012-06-13 inst/examples/cost_of_bias.Rmd
updated runs

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=6, fig.height=6, cache.path="cost_of_bias/", echo=FALSE or`

@@

``` {r setup, echo=FALSE}
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())
````

@@

```{r }
z_g <- function() 1 
z_m <- function() 1 
z_i <- function() 1 
````

>>>>

`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=6, fig.height=6, cache.path="cost_of_bias/", verbose=TRUE  or`

@@

``` {r setup, echo=FALSE, cache=FALSE}
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
````

@@

```{r }
sigma_g <- 0.0    # Noise in population growth
z_g <- function() 1 
z_m <- function() 1 
z_i <- function() 1 
````

### 2012-06-13 inst/examples/value_of_information.Rmd
reckless driver scenario
updated runs

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=5 or`

@@

``` {r  setup, echo=FALSE}
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())
````

@@

Note that the `pdg_control` pacakge already has a definition for the `BevHolt` function, (typing the function name prints the function)

@@

Of course we could pass in any custom function of stocksize `x`, harvest `h` and parameter vector `p` in place of `BevHolt`.  Note that we would need to write this function explicitly so that it can take vector values of `x` (i.e. uses `sapply`), an annoying feature of `R` for users comming from Matlab.

@@

``` {r noisefns}
sigma_g <- 0.01    # Noise in population growth
sigma_m <- 0.0     # noise in stock assessment measurement
sigma_i <- 0.0     # noise in implementation of the quota
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
````
Find the transition matrix

>>>>

`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, cache.path="value_of_information/", verbose=TRUE or`

@@

``` {r  setup, echo=FALSE, cache=FALSE}
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())
````

@@

Note that the `pdg_control` package already has a definition for the `BevHolt` function, (typing the function name prints the function)

@@

Of course we could pass in any custom function of stocksize `x`, harvest `h` and parameter vector `p` in place of `BevHolt`.  Note that we would need to write this function explicitly so that it can take vector values of `x` (i.e. uses `sapply`), an annoying feature of `R` for users coming from Matlab.

@@

``` {r noisefns}
sigma_g <- 0.01    # Noise in population growth
sigma_m <- 0.0     # noise in stock assessment measurement
sigma_i <- 0.0     # noise in implementation of the quota
z_g <- function() 1 
z_m <- function() 1
z_i <- function() 1 
````
Find the transition matrix
